\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\ifdefined\pdfgentounicode\input{glyphtounicode}\fi


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\ifdefined\pdfgentounicode\pdfgentounicode=1\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Yash  Bhardwaj} \\ \vspace{1pt}
    \small +91-8178084472 $|$ \href{mailto:yashbhardwaj911@gmail.com}{\underline{Email}} $|$
    \href{https://www.linkedin.com/in/yash-bhardwaj-x/}{\underline{LinkedIn}} $|$
    \href{https://github.com/y4shb}{\underline{Github}} $|$
    \href{https://y4shbhardwaj.com/}{\underline{Website}}
\end{center}


%-----------Summary-----------
% \section{Professional Summary}
\small Senior Software Development Engineer with upto 5 years designing, building, \& shipping \textbf{high-availability, scalable platforms} and \textbf{automation pipelines}. Skilled in \textbf{distributed systems, microservices, cloud (AWS/Azure), CI/CD, \& observability}, with hands-on expertise in \textbf{Python, Java, JavaScript/TypeScript, Angular/React}. Passionate about clean architecture, developer productivity, and delivering secure, \textbf{customer-centric software solutions.}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AMD}{September 2025 -- Present}
      {Senior Software Development Engineer, DCAuto Platform}{ }
      \resumeItemListStart
        \resumeItem{Developed features for \textbf{DCAuto}, AMD's internal platform automating \textbf{firmware CI/regression testing} for \textbf{AMD MI450 data center GPUs} by orchestrating deployments \& workloads across physical \textbf{Systems(SUTs)}.}
        \resumeItem{Architected and shipped \textbf{PSN self check-in (HKYSY mode)} with idempotency and fallbacks to harden DCAuto deploy/submit workflows and recover from transient infra/SUT failures.}
        \resumeItem{Built \textbf{DCAutoAI / Sherlog Holmes} (AMD AI Hackathon): 5-stage failure triage for GPU firmware validation (\textbf{50,000+ line} logs) using embeddings + \textbf{FAISS} vector search and \textbf{LLM} root-cause analysis; shipped Flask v3 APIs with \textbf{Celery/Azure Service Bus}, MongoDB, and Teams alerts.} \\
      \resumeItemListEnd

      \textbf{Tech Stack}: Python, Flask, Celery, WebSockets, PostgreSQL, MongoDB, Redis, Azure, CI/CD, Docker, FAISS

    \resumeSubheading
      {Qualcomm}{August 2022 -- June 2025}
      {Software Engineer}{ }
      \resumeItemListStart
        \resumeItem{Designed and built \textbf{scalable, high-availability} systems for \textbf{Qualcomm Software Center (QSC)}, an Electron app built using \textbf{NodeJS, Angular, \& TypeScript}, ensuring seamless device-driver delivery for global OEMs.}
        \resumeItem{\textbf{Delivered the first MacOS universal release for QSC}, single-handedly resolving cross-platform dependencies and ensuring a frictionless rollout to \textbf{Fortune 500 clients like Apple, Samsung, and Bosch.}}
        \resumeItem{Owned the \textbf{end-to-end release management} process, automating \textbf{CI/CD pipeline} (Jenkins + AWS), packaging multiple modules, and enhancing \textbf{code quality} via rigorous \textbf{design/code reviews.}}
        \resumeItem{Architected \textbf{AWS-based deployment pipelines} and integrated logging/monitoring, reducing software release times by \textbf{50\%} and improving incident response.}
        \resumeItem{Collaborated daily with engineering managers and enterprise clients \textbf{(eg. Microsoft, AT\&T, BMW)} to triage bugs,
        plan and build \textbf{key UI feature releases}, and ensure stability.} \\

      \resumeItemListEnd

      \textbf{Tech Stack}: NodeJS, Angular, Electron, Javascript, AWS, High-Availability Systems, CI/CD, Python

    \resumeSubheading
      {Licious}{June 2021 –- July 2022}
      {Software Development Engineer }{ }
      \resumeItemListStart
        \resumeItem{Designed and \textbf{implemented scalable microservices} in Java (Spring Boot) and PHP, \textbf{optimizing high-volume order processing} for a nationwide POS system.}
        \resumeItem{Architected RESTful APIs, reducing API response times by \textbf{25\%} across {100+ delivery centers.}}
        \resumeItem{Built an \textbf{automated unit testing framework} using REST-assured, enhancing test coverage.}
        \resumeItem{Automated \textbf{infrastructure deployment} with Docker and Kubernetes, streamlining development workflows.} \\

    \resumeItemListEnd

    \textbf{Tech Stack}: Java, SpringBoot, PHP, Microservices, High-Traffic Systems, Docker, Kubernetes, AWS \\

  \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BITS Pilani KK Birla Goa Campus}{2017 -- 2021}
      {Bachelor of Engineering(Hons.)}{ }
  \resumeSubHeadingListEnd




%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{High-Scalability System Design, QSC } $|$ {\textbf{Qualcomm}}}{ }
          \resumeItemListStart
            \resumeItem{Engineered \textbf{high-performance API gateways}, assisted in \textbf{Axway-to-Apigee migration for QSC,} handling millions of requests per second.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Prognostics Modeling of Part Degradation in Turbofan Engines} $|$ {\textbf{Thesis, BITS Pilani}}}{ }
          \resumeItemListStart
            \resumeItem{Designed LSTMs and ensemble based AI models using TensorFlow, achieving an R2 score of 0.75 for turbofan engine \textbf{life-cycle prediction.}}
          \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{DeepFake Generation and Detection Using GANs} $|$ {\textbf{BITS Pilani}}}{ }
      \resumeItemListStart
        \resumeItem{Modelled GANs for generating clear, recognizable images using PyTorch, achieving an 80\% accuracy.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Python, Java, SpringBoot, JavaScript, TypeScript, React, Angular, NodeJS, Flask, SQL, PostgreSQL, Redis, AWS, Azure, Docker, Kubernetes, CI/CD, JIRA, Monitoring, Observability, Firmware Test Automation, AI Triage
     }}
 \end{itemize}


%-------------------------------------------
\end{document}
